Functional diversity improves tropical forest recovery from disturbance shifting from complementarity to selection effect (to rework)

### 2018-07-16 S3-RNE.Rmd
Draft 0.1.9006 Supplementary: Resilience indice, Linear models, Biodiversity results

---
title: "Supplementary material S2: Biodiversity net effect and resilience"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

>>>>

---
title: "Supplementary material S3: Biodiversity net effect and resilience"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

### 2018-07-16 S4-LM.Rmd
Draft 0.1.9006 Supplementary: Resilience indice, Linear models, Biodiversity results

---
title: "Supplementary material S3: Linear models"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

@@

Secondly tfor $structure$ and $production$ variables models \@ref(eq:m1) and \@ref(eq:m2) gives similar results, at the exception of the effect of $FDis.LMA$ in $production$ resilience. So I think we can keep only model \@ref(eq:m2) keeping in mind the effect of $FDis.LMA$ on $production$.

>>>>

---
title: "Supplementary material S4: Linear models"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

@@

Secondly, for $structure$ and $production$ variables models \@ref(eq:m1) and \@ref(eq:m2) gives similar results, at the exception of the effect of $FDis.LMA$ in $production$ resilience. So I think we can keep only model \@ref(eq:m2) keeping in mind the effect of $FDis.LMA$ on $production$.

### 2018-07-16 draft.Rmd
Draft 0.1.9006 Supplementary: Resilience indice, Linear models, Biodiversity results

```{r config, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls()); invisible(gc())
library(knitr)
library(kableExtra)
if(knitr:::is_html_output()) options(knitr.table.format = "html") 
if(knitr:::is_latex_output()) options(knitr.table.format = "latex") 
library(tidyverse)
library(broom)
theme_set(bayesplot::theme_default())
opts_chunk$set( echo = F, message = F, warning = F, 
                fig.height = 8, fig.width = 8,
                cache = T, cache.lazy = F)
```

@@

```{r gIeq, echo=FALSE, fig.cap='Ecosystem recovery after 600 years with taxonomic and functional diversity for different levels of disturbance. Cumulative integral from ecosystem distance to forest structure equilibrium after 600 years was represented against functional diversity [FDiv, @villeger_new_2008] for different level of disturbance (25, 50 and 75% of total basal area); dot shapes represents the species richness whereas dot color represents functional evenness [FEve, @villeger_new_2008]. Solid lines and grey areas show fitted relationships with their mean and variance of the form $Ieq_600 = FDiv + \\epsilon$.', cache=TRUE, fig.width=12}
Ieq %>% 
  left_join(., doe, by = 'sim') %>% 
  filter(time == 600) %>% 
  ggplot(aes(x = FDiv, y = Ieq.structure, label = sim)) + 
  geom_smooth(method = 'lm', alpha = 0.3, colour= 'grey') +
  geom_point(aes(shape = richness, color = FEve)) +
  facet_wrap(~disturbance, scales = "free", labeller = 'label_both') + 
  xlab('Functional diversity (FDiv)') +
  ylab('Cummulative integral from ecosystem 
       distance to forest structure equilibrium after 600 years') +
  scale_shape_discrete('Species\nrichness\n(SR)') +
  scale_color_continuous('Functional\nevenness\n(FEve)')
```

@@

```{r gBE, echo=FALSE, fig.cap='recovery of complementarity and selection effects. Complementarity effect (CE) and selection effect (SE) where normalized by control net effect (NEc), thus measuring their recovery over time. Solid lines represents the mean value whereas areas represents the interval of values among simulations.', cache=TRUE, fig.width=12}
BEresilience %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  # filter(BE %in% c('SE', 'CE')) %>% 
  group_by(time, BE, disturbance, richness) %>%
  summarise(qt1 =quantile(agb, probs=0.05),
            qt2 =quantile(agb, probs=0.75),
            mean=mean(agb),
            n=n()) %>% 
  ggplot(aes(x = time)) +
  geom_hline(yintercept = 1, color = 'red') +
  geom_hline(yintercept = 0, color = 'blue') +
  geom_ribbon(aes(ymin = qt1, ymax = qt2, fill = BE), alpha = 0.3) +
  geom_line(aes(y = mean, color = BE)) +
  facet_grid(richness ~ disturbance, labeller = 'label_both') +
  xlab('Time (years)') +
  ylab('Recovery of aboveground biomass net effect')
```

@@

* Supplementary materials S1: Leaf lifespan model
    + [HTML](S1.html)
    + [PDF](S1.pdf)
* Supplementary materials S2: Disturbance simulations
    + [HTML](S2.html)
    + [PDF](S2.pdf)

>>>>

```{r config, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls()); invisible(gc())
library(knitr)
library(kableExtra)
if(knitr:::is_html_output()) options(knitr.table.format = "html") 
if(knitr:::is_latex_output()) options(knitr.table.format = "latex") 
library(tidyverse)
library(broom)
theme_set(bayesplot::theme_default())
opts_chunk$set( echo = F, message = F, warning = F, 
                fig.height = 8, fig.width = 12,
                cache = T, cache.lazy = F)
```

@@

```{r gIeq, echo=FALSE, fig.cap='Ecosystem recovery after 600 years with taxonomic and functional diversity for different levels of disturbance. Cumulative integral from ecosystem distance to forest structure equilibrium after 600 years was represented against functional diversity [FDiv, @villeger_new_2008] for different level of disturbance (25, 50 and 75% of total basal area); dot shapes represents the species richness whereas dot color represents functional evenness [FEve, @villeger_new_2008]. Solid lines and grey areas show fitted relationships with their mean and variance of the form $Ieq_600 = FDiv + \\epsilon$.', cache=TRUE}
Ieq %>% 
  left_join(., doe, by = 'sim') %>% 
  filter(time == 600) %>% 
  ggplot(aes(x = FDiv, y = Ieq.structure, label = sim)) + 
  geom_smooth(method = 'lm', alpha = 0.3, colour= 'grey') +
  geom_point(aes(shape = richness, color = FEve)) +
  facet_wrap(~disturbance, scales = "free", labeller = 'label_both') + 
  xlab('Functional diversity (FDiv)') +
  ylab('Cummulative integral from ecosystem 
       distance to forest structure equilibrium after 600 years') +
  scale_shape_discrete('Species\nrichness\n(SR)') +
  scale_color_continuous('Functional\nevenness\n(FEve)')
```

@@

```{r gBE, echo=FALSE, fig.cap='recovery of complementarity and selection effects. Complementarity effect (CE) and selection effect (SE) where normalized by control net effect (NEc), thus measuring their recovery over time. Solid lines represents the mean value whereas areas represents the interval of values among simulations.', cache=TRUE}
BEresilience %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  # filter(BE %in% c('SE', 'CE')) %>%
  group_by(time, BE, disturbance, richness) %>%
  summarise(qt1 =quantile(agb, probs=0.05),
            qt2 =quantile(agb, probs=0.75),
            mean=mean(agb),
            n=n()) %>% 
  ggplot(aes(x = time)) +
  geom_hline(yintercept = 1, color = 'red') +
  geom_hline(yintercept = 0, color = 'blue') +
  geom_ribbon(aes(ymin = qt1, ymax = qt2, fill = BE), alpha = 0.3) +
  geom_line(aes(y = mean, color = BE)) +
  facet_grid(disturbance ~ richness, labeller = 'label_both') +
  xlab('Time (years)') +
  ylab('Recovery of aboveground biomass net effect')
```

@@

* Supplementary materials S1: Leaf lifespan model
    + [HTML](S1-LL.html)
    + [PDF](S1-LL.pdf)
* Supplementary materials S2: Resilience indice
    + [HTML](S2-Resilience.html)
    + [PDF](S2-Resilience.pdf)
* Supplementary materials S3: Biodiversity net effect and resilience 
    + [HTML](S3-RNE.html)
    + [PDF](S3-RNE.pdf)
* Supplementary materials S4: Linear models
    + [HTML](S4-LM.html)
    + [PDF](S4-LM.pdf)
* Supplementary materials S5: Biodiversity effect results
    + [HTML](S5-Biodiversity.html)
    + [PDF](S5-Biodiversity.pdf)
